Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2020-01-08 2016-Weak-FH-Bisim/WeakBisim.tex
pepm et argument subst

@@

\TODO{J'ai un probleme ici, comme on a dit que les AO etaient satures par substitution, ils sont par nature infinis... Donc le theoreme, tel qu'il est exprime, est vrai, mais inapplicable. La solution est dans le papier de PEPM, mais complique a expliquer...}
\TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}

If we assume that everything is finite (states and transitions in the
open automata, and the predicates in $\mathcal{R}$, then it is easy to
prove that it is decidable whether a relation is a 
FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).

>>>>

\LUDO{I added this paragraph}
Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed). However an open automaton is characterized by a  subset of these open transition which is sufficient to generate, by substitution the other ones. In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions.

@@

\TODO{J'ai un probleme ici, comme on a dit que les AO etaient satures par substitution, ils sont par nature infinis... Donc le theoreme, tel qu'il est exprime, est vrai, mais inapplicable. La solution est dans le papier de PEPM, mais complique a expliquer...}
\TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}
\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le papier PEPM?}
If we assume that everything is finite (states and transitions in the
open automata, and the predicates in $\mathcal{R}$, then it is easy to
prove that it is decidable whether a relation is a 
FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).
